Detecting TravisCI Misconfiguration

### 2016-08-22 Travis/main.tex
startign on time

>>>>

\subsection{Learning from Temporal properties}

An intersting extension to ConfigC on a theortical side is to look at the temporal relations between commits.
In addition to knowledge of which .travis.yml files are correct, we can also know what changes made such a file correct (or incorrect).
As a rough outline of a formalism, take each commit as a tuple $(T_i , C_i , S_i)$
